Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2015-07-18 mard-survey.tex
2015.06.25 (Vassilis) Minor changes to "thanks" and "bio" sections.

\author{Vassilis Moustakas,
        H\"useyin Akcan,
        Mema Roussopoulos,
        and~Alex Delis,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{Vassilis Moustakas, Mema Roussopoulos and Alex Delis are 
	with the Department of Informatics and Telecommunications, 
	\emph{University of Athens},
GR15784, Athens, Greece, e-mails: \emph{\{vsmoustakas,mema,ad\}@di.uoa.gr}}% <-this % stops a space
\thanks{H\"useyin Akcan is with the Department of Software Engineering,
\emph{Izmir University of Economics}, 35330 Balcova, Izmir, Turkey, email: \emph{huseyin.akcan@ieu.edu.tr}}% <-this % stops a space
\thanks{Manuscript received April 30, 2015; revised April 30, 2015.}}

@@

\begin{IEEEbiography}{Vassilis Moustakas}
% Biography text here.
is a researcher with the University of Athens in Athens, Greece.
\end{IEEEbiography}

>>>>

\author{Vassilis Moustakas,
        H\"useyin Akcan,
        Mema Roussopoulos,
        and~Alex Delis,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{Vassilis Moustakas is
with \emph{Amazon Development Center Germany GmbH},
DE80807, Munich Germany, email: \emph{vsmoustakas@gmail.com}
(this work was done while a graduate student at the Department of Informatics and Telecommunications, \emph{University of Athens})}% <-this % stops a space
\thanks{H\"useyin Akcan is with the Department of Software Engineering,
\emph{Izmir University of Economics}, 35330 Balcova, Izmir, Turkey, email: \emph{huseyin.akcan@ieu.edu.tr}}% <-this % stops a space
\thanks{Mema Roussopoulos and Alex Delis are 
	with the Department of Informatics and Telecommunications, 
	\emph{University of Athens},
GR15784, Athens, Greece, e-mails: \emph{\{mema,ad\}@di.uoa.gr}}% <-this % stops a space
\thanks{Manuscript received June 28, 2015; revised June 28, 2015.}}

@@

\begin{IEEEbiography}{Vassilis Moustakas}
% Biography text here.
is a software development engineer at Amazon.com and a researcher with the University of Athens in Athens, Greece.
\end{IEEEbiography}
